---
title: "p8105_hw1_hr2569"
author: "Hongzhu Ren"
date: "2023-09-20"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(moderndive)
```

# problem 1

## 1. Dataset interpretation

The dataset describes Hourly meteorological data for LGA, JFK and EWR for the month of January 2013.

```{r data view}
data("early_january_weather")
```

1a. The variables in the dataset are `r colnames(early_january_weather)`

Mean and sd for specific variables are listed below

Variables | mean | sd
--------- | -------- | ---------
*temp* | `r mean(early_january_weather$temp)` | `r sd(early_january_weather$temp)`
*dewp* | `r mean(early_january_weather$dewp)` | `r sd(early_january_weather$dewp)`
*humid* | `r mean(early_january_weather$humid)` | `r sd(early_january_weather$humid)`
*wind_speed* | `r mean(early_january_weather$wind_speed)` | `r sd(early_january_weather$wind_speed)`
*precip* | `r mean(early_january_weather$precip)` | `r sd(early_january_weather$precip)`
*visib* | `r mean(early_january_weather$visib)` | `r sd(early_january_weather$visib)`

1b. The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns

1c. The mean temperature is `r mean(early_january_weather$temp)`

## 2. Scatterplot

Draw a scatterplot of `temp` and `time_hour`.

```{r temp&time_hour_scatterplot}
ggplot(early_january_weather, 
       aes(y = temp, x = time_hour, color = humid)) + 
  geom_point()
```

From the scatterplot, we can see that temperature rises in flucuations over time. And the daily temperature's range were similar.  

Now we save the scatterplot.

```{r save_plot, echo=FALSE}
ggsave("temp_v_time_hour_scatterplot.png")
```


